---
title: "Initial EDA 3"
author: "Isabella and Josh"
date: "2026-04-09"
output: html_document
editor_options: 
  chunk_output_type: console
---


# Libraries
Several R libraries were used for EDA, plotting, file operations, linear regression modeling, etc.
```{r setup, include = FALSE}
library(tidyverse)
library(arrow)
library(here)
library(purrr)
library(stringr)
library(lubridate)
library(DataExplorer)
library(skimr)
library(ggplot2)
library(dplyr)
```

# Read in Data, Select, Filter, Sample, and Mutate/Feature Engineering
#### NYC Yellow Taxi Trip data for 2025 was retrieved from:
https://www.nyc.gov/site/tlc/about/tlc-trip-record-data.page

#### Ingestion
Read in all raw data from 12 parquet files, then read Taxi Zone Lookup file from https://catalog.data.gov/dataset/nyc-taxi-zones-131e4
```{r}
files <- list.files(here("Main data"), pattern = "\\.parquet$", full.names = TRUE)
# get the number of observations
# dim(df_raw)[1] #48,722,602 Over 48M for Jan-Dec 2025

# Read in taxi zone lookup
zone_lookup <- read.csv(here("Additional Data", "NYC_Taxi_Zones.csv"))
```

#### Selection
11 of 20 columns were selected; Columns not selected: VendorID, RatecodeID, store_and_fwd_flag, mta_tax, tolls_amount, improvement surcharge, congestion_surcharge, airport_fee, cbd_congestion_fee, passenger_count

#### Filters

#### Sample 
Data is sampled down to a target n, with an even number of samples from each month

```{r}
# Get the Location IDs that belong to the selected borough
# Note: this may be a dropdown selection in the RShiny app
selected_boroughs <- c("Manhattan", "Queens")
zone_ids <- zone_lookup %>%
  filter(Borough %in% selected_boroughs) %>%
  pull(Location.ID)

# use scientific notation so we can easily change order of magnitude
# this will be useful for verifying scalability
target_n <- 1e4
n_per_file <- ceiling(target_n / length(files))

df_sampled <- map_dfr(files, function(f) {
  
  df <- read_parquet(
    f,
    col_select = c(
      "tpep_pickup_datetime",
      "tpep_dropoff_datetime",
      "fare_amount",
      "trip_distance",
      "tip_amount",
      "total_amount",
      "PULocationID",
      "DOLocationID",
      "payment_type",
      "extra",
      "passenger_count",
      "Airport_fee"
    )
  )
  
  df %>%
    filter(
      # Both pickup and dropoff are in selected borough
      PULocationID %in% zone_ids,
      DOLocationID %in% zone_ids,
      # payment type is 1 (credit card)
      payment_type == 1,
      # fare amount must be greater than 0
      fare_amount >0,
      # pickup and dropoff cannot be the same datetime
      tpep_pickup_datetime != tpep_dropoff_datetime,
      # passenger count is not NA
      # !is.na(passenger_count)
      passenger_count == 1,
      Airport_fee == 0 # cutting out airport trips
    ) %>%
    ## 25,386,827 = over 25M observations after filtering
    # Take an even sample from each file/month
    slice_sample(n = min(nrow(.), n_per_file)) %>%
    mutate(
      source_file = basename(f),
      month = str_extract(basename(f), "\\d{4}-\\d{2}")
    )
})

# Checking if there is an even sample from each of the months
df_sampled %>% count(source_file)
```



# Mutate/Feature Engineering
## Add derived features to the selected, filtered, sampled data.
```{r}
df_final <- df_sampled %>%
  mutate(
    # feature engineering from pickup and dropoff datetime
    month = month(tpep_pickup_datetime),
    tourist_season = as.factor(ifelse(month %in% c(7, 10, 11, 12), '1', '0')),
    pickup_time = ymd_hms(tpep_pickup_datetime),
    dropoff_time = ymd_hms(tpep_dropoff_datetime),
    pickup_hour = hour(pickup_time),
    dropoff_hour = hour(dropoff_time),
    pickup_date = as_date(pickup_time),
    dropoff_date = as_date(dropoff_time),
    pickup_weekday_num = wday(pickup_time), # 1 = Sunday by default
    dropoff_weekday_num = wday(dropoff_time), # 1 = Sunday by default
    pickup_weekday_name = wday(pickup_time, label = TRUE, abbr = TRUE),
    dropoff_weekday_name = wday(dropoff_time, label = TRUE, abbr = TRUE),
    # Calculate trip time in minutes
    trip_minutes = interval(pickup_time, dropoff_time) / minutes(1),
    # trip speed in miles per hour
    trip_speed_mph = 60* trip_distance / trip_minutes,
    
    # Looking at Tip %
    # we already filter to fare_amount >0, so NA/inf handling is no longer needed
    # tip_pct = if_else(fare_amount > 0, tip_amount / fare_amount, NA_real_),
    # Capping Extreme Tip % Values between 0 and 100 whenever fare amount is too low
    # tip_pct = if_else(tip_pct < 0 | tip_pct > 1, NA_real_, tip_pct)
    tip_pct = 100 * tip_amount / fare_amount
  )

```


# Skim Final Data
```{r}
skim(df_final)
plot_intro(df_final)
plot_missing(df_final)
# see datatype, length, samples of each column
str(df_final)
# see counts of each level in passenger_count
table(df_final$passenger_count)
hist(df_final$trip_speed_mph)
hist(df_final$fare_amount)
hist(df_final$tip_amount)
hist(df_final$trip_minutes)
hist(df_final$trip_distance)
plot(df_final$PULocationID, df_final$tip_amount)
plot(df_final$tourist_season, df_final$tip_amount)
plot(df_final$trip_speed_mph, df_final$tip_amount)
# plot(df_final$passenger_count, df_final$tip_amount)

# look at tip percent in df final
df_final %>%
  summarise(
    mean_tip = mean(tip_amount, na.rm = TRUE),
    median_tip = median(tip_amount, na.rm = TRUE),
    mean_tip_pct = mean(tip_pct, na.rm = TRUE),
    median_tip_pct = median(tip_pct, na.rm = TRUE)
  )
```

# Plots
```{r}

theme_taxi <- function() {
  theme_minimal(base_size = 14) +
    theme(
      plot.background = element_rect(fill = "#FFF200", color = NA),  # taxi yellow
      panel.background = element_rect(fill = "white", color = NA),
      panel.grid.major = element_line(color = "grey80", size = 0.3),
      panel.grid.minor = element_blank(),
      
      plot.title = element_text(face = "bold", size = 18, color = "black"),
      axis.title = element_text(face = "bold", color = "black"),
      axis.text = element_text(color = "black"),
      
      axis.line = element_line(color = "black"),
      legend.position = "top"
    )
}

# note: there are several trips where tip is 100 - 700%, but it's uncommon

# Distribution of tip percentage
ggplot(df_final, aes(x = tip_pct)) +
  geom_histogram(
    bins = 100,
    fill = "black",
    color = "#FFF200",
    linewidth = 0.3
  ) +
  labs(
    title = "Distribution of Tip Percentage",
    x = "Tip Percentage",
    y = "Count"
  ) +
  # shrink the x coord because we can't see the outliers anyway
  coord_cartesian(xlim = c(0, 150)) +
  theme_taxi()


# Tip percentage by weekday
# Note: do not filter out outliers on a boxplot - that's the main point
ggplot(df_final, aes(x = pickup_weekday_name, y = tip_pct)) +
  geom_boxplot() +
  labs(
    title = "Tip Percentage by Pickup Weekday",
    x = "Weekday",
    y = "Tip Percentage"
  )+
  theme_taxi()

# Tip percentage vs trip distance
ggplot(df_final, aes(x = trip_distance, y = tip_pct)) +
  geom_point(alpha = 0.1, shape = "o") +
  geom_smooth(method = "lm",
              formula = y ~ splines::bs(x, 3),
              linewidth = 0.9,
              color = "black",
              linetype = "dashed",
              se = FALSE) +
  labs(
    title = "Tip Percentage vs Trip Distance",
    x = "Trip Distance (miles)",
    y = "Tip Percentage"
  )+
  coord_cartesian(xlim = c(0, 10),
                  ylim = c(0, 100)) +
  theme_taxi()

# Average tip percentage by payment type
# df_final %>%
#   group_by(payment_type) %>%
#   summarise(avg_tip_pct = mean(tip_pct, na.rm = TRUE)) %>%
#   ggplot(aes(x = factor(payment_type), y = avg_tip_pct)) +
#   geom_col() +
#   labs(
#     title = "Average Tip Percentage by Payment Type",
#     x = "Payment Type",
#     y = "Average Tip Percentage"
#   )

# Tip % vs fare amount
ggplot(df_final, aes(x = fare_amount, y = tip_pct)) +
  geom_point(alpha = 0.1, shape = "o") +
  geom_smooth(
              # formula = y ~ splines::bs(x, 2), 
              linewidth = 0.9,
              color = "black",
              linetype = "dashed",
              se = FALSE) +
  coord_cartesian(xlim = c(0,60),
                  ylim = c(0, 100)) +
  labs(
    title = "Tip Percentage vs Fare Amount",
    x = "Fare Amount",
    y = "Tip Percentage"
  )+
  theme_taxi()
```

# EDA for Tipping Amount
```{r}
# Distribution of tip amount
ggplot(df_final, aes(x = tip_amount)) +
  geom_histogram(bins = 100,
    fill = "black",
    color = "#FFF200",) +
    coord_cartesian(xlim = c(0,20)) +
  labs(
    title = "Distribution of Tip Amount",
    x = "Tip Amount",
    y = "Count"
  ) + 
  theme_taxi()

# # Tip amount by payment type
# ggplot(df_final, aes(x = factor(payment_type), y = tip_amount)) +
#   geom_boxplot() +
#   labs(
#     title = "Tip Amount by Payment Type",
#     x = "Payment Type",
#     y = "Tip Amount"
#   )

# Tip amount vs fare amount
ggplot(df_final, aes(x = fare_amount, y = tip_amount)) +
  geom_point(alpha = 0.1,
             shape = "o") +
  geom_smooth(method = "lm",
              linewidth = 0.9,
              color = "black",
              linetype = "dashed",
              se = FALSE) +
  coord_cartesian(xlim = c(0,75),
                  ylim = c(0,20)) +
  labs(
    title = "Tip Amount vs Fare Amount",
    x = "Fare Amount",
    y = "Tip Amount"
  )+
  theme_taxi()

# Tip amount vs trip distance
ggplot(df_final, aes(x = trip_distance, y = tip_amount)) +
  geom_point(alpha = 0.1,
             shape = "o") +
  geom_smooth(method = "lm",
              linewidth = 0.9,
              color = "black",
              linetype = "dashed",
              se = FALSE) +
    coord_cartesian(xlim = c(0,10),
                  ylim = c(0,20)) +
  labs(
    title = "Tip Amount vs Trip Distance",
    x = "Trip Distance (miles)",
    y = "Tip Amount"
  ) +
  theme_taxi()

# Tip amount vs trip duration
ggplot(df_final, aes(x = trip_minutes, y = tip_amount)) +
  geom_point(alpha = 0.1,
             shape = "o") +
  geom_smooth(method = "lm",
              formula = y ~ splines::bs(x, 2),
              linewidth = 0.9,
              color = "black",
              linetype = "dashed",
              se = FALSE) +
  coord_cartesian(xlim = c(0,50),
                  ylim = c(0,20)) +
  labs(
    title = "Tip Amount vs Trip Duration",
    x = "Trip Duration (minutes)",
    y = "Tip Amount"
  ) +
  theme_taxi()
## Comment: Two VERY LONG trips DRASTICALLY changed slope of regression line

```

# See how tip amount varies over time
```{r}
# Tip amount by weekday
ggplot(df_final, aes(x = pickup_weekday_name, y = tip_amount)) +
  geom_boxplot() +
  labs(
    title = "Tip Amount by Pickup Weekday",
    x = "Weekday",
    y = "Tip Amount"
  ) +
  theme_taxi()

# Tip amount by month
df_final %>%
  group_by(month) %>%
  summarise(avg_tip_amt = mean(tip_amount, na.rm = TRUE)) %>%
  ggplot(aes(x = factor(month), y = avg_tip_amt)) +
  geom_col() +
  labs(
    title = "Average Tip Amount by Month",
    x = "Month",
    y = "Average Tip Amount"
  )+
  theme_taxi()
```

# Look at Tourist Season: July, Oct-Dec
```{r}
# Tip amount vs tourist season
df_final %>%
  group_by(tourist_season) %>%
  summarise(avg_tip_amt = mean(tip_amount, na.rm = TRUE)) %>%
  ggplot(aes(x = factor(tourist_season), y = avg_tip_amt)) +
  geom_col() +
  labs(
    title = "Average Tip Amount by Tourist Season",
    x = "Tourist Season",
    y = "Average Tip Amount"
  )+
  theme_taxi()

# Tip amount vs tourist season - higher amounts are more common in tourist season
df_final %>%
  ggplot(aes(x = tip_amount, color = factor(tourist_season))) +
  geom_density(linewidth = 0.75) +
  labs(
    title = "Tip Amount Dist in Tourist Season vs Off-Season",
    x = "Tip Amount",
    color = "Tourist Season"
  ) +
  theme_taxi()

# Tip percent vs tourist season - does not seem to vary by tourist season
df_final %>%
  ggplot(aes(x = tip_pct, color = factor(tourist_season))) +
  geom_density(linewidth = 0.75) +
  ggtitle("Tip Percent Dist in Tourist Season vs Off-Season") +
  xlab("Tip Percent") +
  theme_taxi()
```

``` {r}

```


# Looking at Correlation
```{r}
numeric_vars <- df_final %>%
  select(
    fare_amount,
    trip_distance,
    extra,
    pickup_hour,
    dropoff_hour,
    trip_minutes,
    trip_speed_mph,
    tip_amount,
    pickup_weekday_num,
    # tourist_season
  )

cor_matrix <- cor(numeric_vars, use = "pairwise.complete.obs")
cor_matrix

# Heatmap Version
corrplot::corrplot(cor_matrix, method = "color", type = "upper")

plot_correlation(numeric_vars)
```

# Possible First Regression Model
```{r}
fit_tip <- lm(
  tip_amount ~ fare_amount + 
    trip_distance + 
    trip_minutes +
    pickup_hour + 
    pickup_weekday_name +
    extra + month,
  data = df_final
)

summary(fit_tip)

# Checks for multicolinearity among predictors by looking at VIF
library(car)
car::vif(fit_tip)
```




### MODELING


# Model 1 (ROUGH)
```{r}
# Listing Columns
names(df_final)


# Clean obvious bad records before modeling
# these are already filtered in df_final (see histograms in skim section)
df_clean <- df_final %>%
  filter(
    tip_amount > 0,
    tip_amount < quantile(tip_amount, 0.99),
    fare_amount > 0,
    trip_distance > 0,
    trip_minutes > 0
  )

 df_clean = df_clean %>% mutate(
    month = factor(month),
    pickup_hour = factor(pickup_hour),
    pickup_weekday_name = factor(pickup_weekday_name, ordered = FALSE))

# Creating DF subset
df_model1 = df_clean %>% 
  select(tip_amount,
         fare_amount,
         trip_distance,
         # month,
         extra,
         trip_minutes,
         # tourist_season,
         )


# MODEL 1
# log1p does log(1+x) so it helps when vairable is 0
# but now doing just log
fit1 <- lm(log(tip_amount)~fare_amount + I(fare_amount^2) +
    trip_distance + extra + trip_minutes, data = df_model1)
summary(fit1)

# Assumptions
par(mfrow = c(2, 2))
plot(fit1)
par(mfrow = c(1, 1))


# RMSE
rmse = sqrt(mean(residuals(fit1)^2))
rmse

# MAE
mae = mean(abs(residuals(fit1)))
mae


# Model 2
fit2 <- lm(
  log(tip_amount) ~ fare_amount + I(fare_amount^2) + extra,
  data = df_model1
)
summary(fit2)


# Outliers
df_o = df_final[c(4000, 10000, 4998),] 

```






