---
title: "Project V1"
author: "Josh"
date: "2026-04-12"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Libraries
Several R libraries were used for EDA, plotting, file operations, linear regression modeling, etc.
```{r setup, include = FALSE}
library(tidyverse)
library(arrow)
library(here)
library(purrr)
library(stringr)
library(lubridate)
library(DataExplorer)
library(skimr)
library(ggplot2)
library(dplyr)
```

# Read in Data, Select, Filter, Sample, and Mutate/Feature Engineering
#### NYC Yellow Taxi Trip data for 2025 was retrieved from:
https://www.nyc.gov/site/tlc/about/tlc-trip-record-data.page

#### Ingestion
Read in all raw data from 12 parquet files, then read Taxi Zone Lookup file from https://catalog.data.gov/dataset/nyc-taxi-zones-131e4
```{r}
files <- list.files(here("Main data"), pattern = "\\.parquet$", full.names = TRUE)
# get the number of observations
# dim(df_raw)[1] #48,722,602 Over 48M for Jan-Dec 2025

# Read in taxi zone lookup
zone_lookup <- read.csv(here("Additional Data", "NYC_Taxi_Zones.csv"))
```

#### Selection
11 of 20 columns were selected; Columns not selected: VendorID, RatecodeID, store_and_fwd_flag, mta_tax, tolls_amount, improvement surcharge, congestion_surcharge, airport_fee, cbd_congestion_fee, passenger_count

#### Filters

#### Sample 
Data is sampled down to a target n, with an even number of samples from each month

```{r}
# Get the Location IDs that belong to the selected borough
# Note: this may be a dropdown selection in the RShiny app
selected_boroughs <- c("Manhattan", "Queens")
zone_ids <- zone_lookup %>%
  filter(Borough %in% selected_boroughs) %>%
  pull(Location.ID)

# use scientific notation so we can easily change order of magnitude
# this will be useful for verifying scalability
target_n <- 1e4
n_per_file <- ceiling(target_n / length(files))

df_sampled <- map_dfr(files, function(f) {
  
  df <- read_parquet(
    f,
    col_select = c(
      "tpep_pickup_datetime",
      "tpep_dropoff_datetime",
      "fare_amount",
      "trip_distance",
      "tip_amount",
      "total_amount",
      "PULocationID",
      "DOLocationID",
      "payment_type",
      "extra",
      "passenger_count",
      "Airport_fee"
    )
  )
  
  df %>%
    filter(
      # Both pickup and dropoff are in selected borough
      PULocationID %in% zone_ids,
      DOLocationID %in% zone_ids,
      # payment type is 1 (credit card)
      payment_type == 1,
      # fare amount must be greater than 0
      fare_amount >0,
      # pickup and dropoff cannot be the same datetime
      tpep_pickup_datetime != tpep_dropoff_datetime,
      # passenger count is not NA
      # !is.na(passenger_count)
      passenger_count == 1,
      Airport_fee == 0 # cutting out airport trips
    ) %>%
    ## 25,386,827 = over 25M observations after filtering
    # Take an even sample from each file/month
    slice_sample(n = min(nrow(.), n_per_file)) %>%
    mutate(
      source_file = basename(f),
      month = str_extract(basename(f), "\\d{4}-\\d{2}")
    )
})

# Checking if there is an even sample from each of the months
df_sampled %>% count(source_file)
```



# Mutate/Feature Engineering
## Add derived features to the selected, filtered, sampled data.
```{r}
df_final <- df_sampled %>%
  mutate(
    # feature engineering from pickup and dropoff datetime
    month = month(tpep_pickup_datetime),
    tourist_season = as.factor(ifelse(month %in% c(7, 10, 11, 12), '1', '0')),
    pickup_time = ymd_hms(tpep_pickup_datetime),
    dropoff_time = ymd_hms(tpep_dropoff_datetime),
    pickup_hour = hour(pickup_time),
    dropoff_hour = hour(dropoff_time),
    pickup_date = as_date(pickup_time),
    dropoff_date = as_date(dropoff_time),
    pickup_weekday_num = wday(pickup_time), # 1 = Sunday by default
    dropoff_weekday_num = wday(dropoff_time), # 1 = Sunday by default
    pickup_weekday_name = wday(pickup_time, label = TRUE, abbr = TRUE),
    dropoff_weekday_name = wday(dropoff_time, label = TRUE, abbr = TRUE),
    # Calculate trip time in minutes
    trip_minutes = interval(pickup_time, dropoff_time) / minutes(1),
    # trip speed in miles per hour
    trip_speed_mph = 60* trip_distance / trip_minutes,
    
    # Looking at Tip %
    # we already filter to fare_amount >0, so NA/inf handling is no longer needed
    # tip_pct = if_else(fare_amount > 0, tip_amount / fare_amount, NA_real_),
    # Capping Extreme Tip % Values between 0 and 100 whenever fare amount is too low
    # tip_pct = if_else(tip_pct < 0 | tip_pct > 1, NA_real_, tip_pct)
    tip_pct = 100 * tip_amount / fare_amount
  )

```


# Skim Final Data
```{r}
skim(df_final)
plot_intro(df_final)
plot_missing(df_final)
# see datatype, length, samples of each column
str(df_final)
# see counts of each level in passenger_count
table(df_final$passenger_count)
hist(df_final$trip_speed_mph)
hist(df_final$fare_amount)
hist(df_final$tip_amount)
hist(df_final$trip_minutes)
hist(df_final$trip_distance)
plot(df_final$PULocationID, df_final$tip_amount)
plot(df_final$tourist_season, df_final$tip_amount)
plot(df_final$trip_speed_mph, df_final$tip_amount)
# plot(df_final$passenger_count, df_final$tip_amount)

# look at tip percent in df final
df_final %>%
  summarise(
    mean_tip = mean(tip_amount, na.rm = TRUE),
    median_tip = median(tip_amount, na.rm = TRUE),
    mean_tip_pct = mean(tip_pct, na.rm = TRUE),
    median_tip_pct = median(tip_pct, na.rm = TRUE)
  )
```

# Plots
```{r}
theme_taxi <- function() {
  theme_minimal(base_size = 14) +
    theme(
      plot.background = element_rect(fill = "#FFF200", color = NA),  # taxi yellow
      panel.background = element_rect(fill = "white", color = NA),
      panel.grid.major = element_line(color = "grey80", size = 0.3),
      panel.grid.minor = element_blank(),
      
      plot.title = element_text(face = "bold", size = 18, color = "black"),
      axis.title = element_text(face = "bold", color = "black"),
      axis.text = element_text(color = "black"),
      
      axis.line = element_line(color = "black"),
      legend.position = "top"
    )
}

# note: there are several trips where tip is 100 - 700%, but it's uncommon

# Distribution of tip percentage
ggplot(df_final, aes(x = tip_pct)) +
  geom_histogram(
    bins = 100,
    fill = "black",
    color = "#FFF200",
    linewidth = 0.3
  ) +
  labs(
    title = "Distribution of Tip Percentage",
    x = "Tip Percentage",
    y = "Count"
  ) +
  # shrink the x coord because we can't see the outliers anyway
  coord_cartesian(xlim = c(0, 150)) +
  theme_taxi()


# Tip percentage by weekday
# Note: do not filter out outliers on a boxplot - that's the main point
ggplot(df_final, aes(x = pickup_weekday_name, y = tip_pct)) +
  geom_boxplot() +
  labs(
    title = "Tip Percentage by Pickup Weekday",
    x = "Weekday",
    y = "Tip Percentage"
  )+
  theme_taxi()

# Tip percentage vs trip distance
ggplot(df_final, aes(x = trip_distance, y = tip_pct)) +
  geom_point(alpha = 0.1, shape = "o") +
  geom_smooth(method = "lm",
              formula = y ~ splines::bs(x, 3),
              linewidth = 0.9,
              color = "black",
              linetype = "dashed",
              se = FALSE) +
  labs(
    title = "Tip Percentage vs Trip Distance",
    x = "Trip Distance (miles)",
    y = "Tip Percentage"
  )+
  coord_cartesian(xlim = c(0, 10),
                  ylim = c(0, 100)) +
  theme_taxi()

# Tip % vs fare amount
ggplot(df_final, aes(x = fare_amount, y = tip_pct)) +
  geom_point(alpha = 0.1, shape = "o") +
  geom_smooth(
              # formula = y ~ splines::bs(x, 2), 
              linewidth = 0.9,
              color = "black",
              linetype = "dashed",
              se = FALSE) +
  coord_cartesian(xlim = c(0,60),
                  ylim = c(0, 100)) +
  labs(
    title = "Tip Percentage vs Fare Amount",
    x = "Fare Amount",
    y = "Tip Percentage"
  )+
  theme_taxi()
```

# EDA for Tipping Amount
```{r}
# Distribution of tip amount
ggplot(df_final, aes(x = tip_amount)) +
  geom_histogram(bins = 100,
    fill = "black",
    color = "#FFF200",) +
    coord_cartesian(xlim = c(0,20)) +
  labs(
    title = "Distribution of Tip Amount",
    x = "Tip Amount",
    y = "Count"
  ) + 
  theme_taxi()

# Tip amount vs fare amount
ggplot(df_final, aes(x = fare_amount, y = tip_amount)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = "lm",
              linewidth = 0.9,
              color = "black",
              linetype = "dashed",
              se = FALSE) +
  coord_cartesian(xlim = c(0,75),
                  ylim = c(0,20)) +
  labs(
    title = "Tip Amount vs Fare Amount",
    x = "Fare Amount",
    y = "Tip Amount"
  )+
  theme_taxi()

# Points where Tip_amt is 0 is in Red
ggplot(df_final, aes(x = fare_amount, y = tip_amount,
                     color = tip_amount == 0)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = "lm",
              linewidth = 0.9,
              color = "black",
              linetype = "dashed",
              se = FALSE,
              inherit.aes = FALSE,
              aes(x = fare_amount, y = tip_amount)) +
  coord_cartesian(xlim = c(0, 75),
                  ylim = c(0, 20)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  labs(
    title = "Tip Amount vs Fare Amount",
    x = "Fare Amount",
    y = "Tip Amount"
  ) +
  theme_taxi() +
  theme(legend.position = "none")


# Tip amount vs trip distance
ggplot(df_final, aes(x = trip_distance, y = tip_amount)) +
  geom_point(alpha = 0.1,
             shape = "o") +
  geom_smooth(method = "lm",
              linewidth = 0.9,
              color = "black",
              linetype = "dashed",
              se = FALSE) +
    coord_cartesian(xlim = c(0,10),
                  ylim = c(0,20)) +
  labs(
    title = "Tip Amount vs Trip Distance",
    x = "Trip Distance (miles)",
    y = "Tip Amount"
  ) +
  theme_taxi()

# Tip amount vs trip duration
ggplot(df_final, aes(x = trip_minutes, y = tip_amount)) +
  geom_point(alpha = 0.1,
             shape = "o") +
  geom_smooth(method = "lm",
              formula = y ~ splines::bs(x, 2),
              linewidth = 0.9,
              color = "black",
              linetype = "dashed",
              se = FALSE) +
  coord_cartesian(xlim = c(0,50),
                  ylim = c(0,20)) +
  labs(
    title = "Tip Amount vs Trip Duration",
    x = "Trip Duration (minutes)",
    y = "Tip Amount"
  ) +
  theme_taxi()
## Comment: Two VERY LONG trips DRASTICALLY changed slope of regression line
```

# See how tip amount varies over time
```{r}
# Tip amount by weekday
ggplot(df_final, aes(x = pickup_weekday_name, y = tip_amount)) +
  geom_boxplot() +
  labs(
    title = "Tip Amount by Pickup Weekday",
    x = "Weekday",
    y = "Tip Amount"
  ) +
  theme_taxi()

# Tip amount by month
df_final %>%
  group_by(month) %>%
  summarise(avg_tip_amt = mean(tip_amount, na.rm = TRUE)) %>%
  ggplot(aes(x = factor(month), y = avg_tip_amt)) +
  geom_col() +
  labs(
    title = "Average Tip Amount by Month",
    x = "Month",
    y = "Average Tip Amount"
  )+
  theme_taxi()
```

# Look at Tourist Season: July, Oct-Dec
```{r}
# Tip amount vs tourist season
df_final %>%
  group_by(tourist_season) %>%
  summarise(avg_tip_amt = mean(tip_amount, na.rm = TRUE)) %>%
  ggplot(aes(x = factor(tourist_season), y = avg_tip_amt)) +
  geom_col() +
  labs(
    title = "Average Tip Amount by Tourist Season",
    x = "Tourist Season",
    y = "Average Tip Amount"
  )+
  theme_taxi()

# Tip amount vs tourist season - higher amounts are more common in tourist season
df_final %>%
  ggplot(aes(x = tip_amount, color = factor(tourist_season))) +
  geom_density(linewidth = 0.75) +
  labs(
    title = "Tip Amount Dist in Tourist Season vs Off-Season",
    x = "Tip Amount",
    color = "Tourist Season"
  ) +
  theme_taxi()

# Tip percent vs tourist season - does not seem to vary by tourist season
df_final %>%
  ggplot(aes(x = tip_pct, color = factor(tourist_season))) +
  geom_density(linewidth = 0.75) +
  ggtitle("Tip Percent Dist in Tourist Season vs Off-Season") +
  xlab("Tip Percent") +
  theme_taxi()
```


# Looking at Correlation Among Numerical Predictors
```{r}
numeric_vars <- df_final %>%
  select(
    fare_amount,
    trip_distance,
    extra,
    pickup_hour,
    dropoff_hour,
    trip_minutes,
    trip_speed_mph,
    tip_amount,
    pickup_weekday_num,
    # tourist_season
  )

cor_matrix <- cor(numeric_vars, use = "pairwise.complete.obs")
cor_matrix

# Heatmap Version
corrplot::corrplot(cor_matrix, method = "color", type = "upper")

plot_correlation(numeric_vars)
```


# MODELING

### Cleaning
```{r}
# Listing Columns
names(df_final)

# Clean obvious bad records before modeling
# these are already filtered in df_final (see histograms in skim section)
df_clean <- df_final %>%
  filter(
    tip_amount > 0,
    tip_amount < quantile(tip_amount, 0.99),
    fare_amount > 0,
    trip_distance > 0,
    trip_minutes > 0
  )

 df_clean = df_clean %>% mutate(
    month = factor(month),
    pickup_hour = factor(pickup_hour),
    pickup_weekday_name = factor(pickup_weekday_name, ordered = FALSE))

# Creating DF subset
df_model1 = df_clean %>% 
  select(tip_amount,
         fare_amount,
         trip_distance,
         extra,
         trip_minutes,
         # month,
         # tourist_season
         )
```

### MODEL 1
```{r}
# log1p does log(1+x) so it helps when vairable is 0
# but now doing just log

fit1 <- lm(log(tip_amount)~fare_amount + I(fare_amount^2) +
    trip_distance + extra + trip_minutes, data = df_model1)
summary(fit1)

# trip_distance & trip_minutes are not seen as significant predictors so we will remove

fit1 <- lm(log(tip_amount)~fare_amount + I(fare_amount^2)  + extra, data = df_model1)
summary(fit1)

# Assumptions
par(mfrow = c(2, 2))
plot(fit1)
par(mfrow = c(1, 1))

# Outliers
df_o = df_final[c(5313),] 
# investigated outlier, but tip amt / % seems to be reaonsable based on fare_amount. Nothing esle seemed out of the ordinary. 

# predicted values on log scale
pred_log <- predict(fit1)

# back-transform to original dollar scale
pred_tip <- exp(pred_log)

# RMSE on original scale
rmse <- sqrt(mean((df_model1$tip_amount - pred_tip)^2))
rmse

# MAE on original scale
mae <- mean(abs(df_model1$tip_amount - pred_tip))
mae

```


### MODEL 2 - Cleaning for Typical Cases
```{r}
df_typical <- df_final %>%
  mutate(tip_pct = tip_amount / fare_amount) %>%
  filter(
    tip_amount > 0,
    fare_amount > 0,
    trip_distance > 0,
    trip_minutes > 0,
    between(fare_amount, quantile(fare_amount, 0.01), quantile(fare_amount, 0.99)),
    between(trip_distance, quantile(trip_distance, 0.01), quantile(trip_distance, 0.99)),
    between(trip_minutes, quantile(trip_minutes, 0.01), quantile(trip_minutes, 0.99)),
    between(tip_pct, quantile(tip_pct, 0.01), quantile(tip_pct, 0.99))
  )

fit2 <- lm(
  log(tip_amount) ~ fare_amount + I(fare_amount^2) + extra,
  data = df_typical
)
summary(fit2)

# Assumptions
par(mfrow = c(2, 2))
plot(fit2)
par(mfrow = c(1, 1))


# predicted values on log scale
pred_log <- predict(fit2)

# back-transform to original dollar scale
pred_tip <- exp(pred_log)

# RMSE on original scale
rmse <- sqrt(mean((df_typical$tip_amount - pred_tip)^2))
rmse

# MAE on original scale
mae <- mean(abs(df_typical$tip_amount - pred_tip))
mae
```



# FOR RAG:
DATA CLEANING
- For our dataset, we are looking at a random sample of 10,008 observations from the NYC Yellow Taxi Trip data for 2025. We randomly sampled 834 observations from each of the months
- We are only looking at data from the following Borough(s): [Manhattan, Queens]. We have the ability to look at other boroughs in the future
- Given credit card was the overwhelming choice for payment_type, we filtered our data set to only look at credit card payments
- Passenger Count is driver-reported so when driver doesnt report count, it will
be a NA. It is commonly understood that when passenger_count is over 1, passengers are less likley to take responsibility to tip. Given these factors, we filtered our dataset to just look at observations where the passenger count was equal to 1. 
- Because airport trips often involve unique fare structures, longer travel distances, and different rider tipping behavior than typical city taxi rides, it is reasonable to exclude them and focus the analysis on non-airport trips so the model reflects a more consistent and representative set of everyday taxi rides.
PLOTS
- Wanted to take detail look at tip percentage (tip %)
- The distribution of tip percentage is heavily right-skewed, with most rides having tip percentages in a moderate range and a small number of rides exhibiting unusually large tip percentages. This long right tail suggests the presence of outliers and indicates that tip percentage is not normally distributed.
- Distribution of tip percentage (tip %) appears relatively consistent throughoout each day of the week
- Appears to be a negative, nonlinear association between fare amount and tip percentage. For smaller fares, tip percentages are much more spread out and can be quite large, while for larger fares, tip percentages tend to be lower and more tightly clustered. This pattern suggests that riders often leave disproportionately high percentage tips on very small fares, whereas tip percentages become more consistent at more moderate levels as fare amount increases.
- Distribution of tip amount appears to be right-skewed. This indicates that small to moderate tips are common, while relatively large tips occur much less frequently.
- Tip amount generally increases as fare amount increases, showing a positive association between the two variables. However, the spread in tip amount also increases for larger fares, and there are several zero-tip rides and some unusually large tips present. Due to the several zero-tip rides across nearly all values for fare amount, we decided to only analyze rides where tip amount was greater than 0. 
- The scatterplot suggests a positive, roughly linear association between trip distance and tip amount, with longer trips generally corresponding to larger tips. Most observations are concentrated among shorter trips with smaller tips, while the spread in tip amount increases as trip distance increases. The plot also shows many rides with zero or very small tips across distances, along with a few unusually large tips that may be considered outliers. A similar case is present with tip amount vs trip duration. 
- 

