---
title: "Project V1"
author: "Josh"
date: "2026-04-12"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Libraries
Several R libraries were used for EDA, plotting, file operations, linear regression modeling, etc.
```{r setup, include = FALSE}
library(tidyverse)
library(arrow)
library(here)
library(purrr)
library(stringr)
library(lubridate)
library(DataExplorer)
library(skimr)
library(ggplot2)
library(dplyr)
library(ggrepel)
library(ggpmisc)
library(scales)
library(readr)
library(forcats)
```

# Read in Data, Select, Filter, Sample, and Mutate/Feature Engineering
#### NYC Yellow Taxi Trip data for 2025 was retrieved from:
https://www.nyc.gov/site/tlc/about/tlc-trip-record-data.page

#### Ingestion
Read in all raw data from 12 parquet files, then read Taxi Zone Lookup file from https://catalog.data.gov/dataset/nyc-taxi-zones-131e4
```{r}
files <- list.files(here("Main data"), pattern = "\\.parquet$", full.names = TRUE)
# get the number of observations
# dim(df_raw)[1] #48,722,602 Over 48M for Jan-Dec 2025

# Read in taxi zone lookup
zone_lookup <- read.csv(here("Additional Data", "NYC_Taxi_Zones.csv"))


```

### Looking into Total Amount
```{r}
# parquet1 = read_parquet('/Users/joshtsamuel/SMU/DS-6306 Doing Data Science/DDS-Project2/Main Data/yellow_tripdata_2025-01.parquet')
# parquet1_test = parquet1[c(1,2),]
# parquet1_test = parquet1_test %>% mutate(TotalAmount2 = fare_amount + extra + mta_tax + tolls_amount + improvement_surcharge + Airport_fee + cbd_congestion_fee + tip_amount)

# Findings: total amount is equal to fare_amount + extra taxes / amounts + tip_amount. It does NOT include however "congestion_surchage"

```


#### Sample 
Data is sampled down to a target n, with an even number of samples from each month

```{r}
set.seed(123)
# Get the Location IDs that belong to the selected borough
# Note: this may be a dropdown selection in the RShiny app
selected_boroughs <- c("Manhattan", "Queens")
zone_ids <- zone_lookup %>%
  filter(Borough %in% selected_boroughs) %>%
  pull(Location.ID)

# use scientific notation so we can easily change order of magnitude
# this will be useful for verifying scalability
target_n <- 1e4
n_per_file <- ceiling(target_n / length(files))

df_sampled <- map_dfr(files, function(f) {
  
  df <- read_parquet(f)
  
  df %>%
    filter(
      PULocationID %in% zone_ids, # Both pickup and dropoff are in selected borough
      DOLocationID %in% zone_ids,
      payment_type == 1, # payment type is 1 (credit card)
      fare_amount >0, # fare amount must be greater than 0
      total_amount >0,
      tpep_pickup_datetime != tpep_dropoff_datetime, # pickup and dropoff cannot be the same datetime
      passenger_count == 1, # passenger count is only 1 
      Airport_fee == 0 # cutting out airport trips
    ) %>%
    ## 25,386,827 = over 25M observations after filtering
    # Take an even sample from each file/month
    slice_sample(n = min(nrow(.), n_per_file)) %>%
    mutate(
      source_file = basename(f),
      month = str_extract(basename(f), "\\d{4}-\\d{2}")
    )
})

# Checking if there is an even sample from each of the months
df_sampled %>% count(source_file)

# write df_sampled to csv
# write_csv(df_sampled, here("R Shiny", "df_sampled.csv"))


# selecting only specific columns
df_sampled = df_sampled %>% select(
      "tip_amount",
      "tpep_pickup_datetime",
      "tpep_dropoff_datetime",
      "fare_amount",
      "trip_distance",
      "total_amount",
      "PULocationID",
      "DOLocationID",
      "payment_type",
      "extra",
      "passenger_count",
      "Airport_fee",
      "source_file",
      "month"
)

```



# Mutate/Feature Engineering
## Add derived features to the selected, filtered, sampled data.
```{r}
df_final <- df_sampled %>%
  mutate(
    # feature engineering from pickup and dropoff datetime
    month = month(tpep_pickup_datetime),
    tourist_season = as.factor(ifelse(month %in% c(7, 10, 11, 12), '1', '0')),
    pickup_time = ymd_hms(tpep_pickup_datetime),
    dropoff_time = ymd_hms(tpep_dropoff_datetime),
    pickup_hour = hour(pickup_time),
    dropoff_hour = hour(dropoff_time),
    pickup_date = as_date(pickup_time),
    dropoff_date = as_date(dropoff_time),
    pickup_weekday_num = wday(pickup_time), # 1 = Sunday by default
    dropoff_weekday_num = wday(dropoff_time), # 1 = Sunday by default
    pickup_weekday_name = wday(pickup_time, label = TRUE, abbr = TRUE),
    dropoff_weekday_name = wday(dropoff_time, label = TRUE, abbr = TRUE),
    # Calculate trip time in minutes
    trip_minutes = interval(pickup_time, dropoff_time) / minutes(1),
    # trip speed in miles per hour
    trip_speed_mph = 60* trip_distance / trip_minutes,
    
    # Looking at Tip %
    # we already filter to fare_amount >0, so NA/inf handling is no longer needed
    # tip_pct = if_else(fare_amount > 0, tip_amount / fare_amount, NA_real_),
    # Capping Extreme Tip % Values between 0 and 100 whenever fare amount is too low
    # tip_pct = if_else(tip_pct < 0 | tip_pct > 1, NA_real_, tip_pct)
    tip_pct = 100 * tip_amount / fare_amount # SHOULD WE SWITCH to Total_Amount
  )

df_rshiny = df_final %>% select(-pickup_time, -dropoff_time, -pickup_hour, -dropoff_hour, -pickup_date, -dropoff_date, -pickup_weekday_num, -dropoff_weekday_num)



# writing csv file for R shiny
write_csv(df_rshiny, here("R Shiny", "df_rshiny.csv"))
```


# Skim Final Data
```{r}
skim(df_final)
plot_intro(df_final)
plot_missing(df_final)
# see datatype, length, samples of each column
str(df_final)
# see counts of each level in passenger_count
table(df_final$passenger_count)
hist(df_final$trip_speed_mph)
plot(df_final$PULocationID, df_final$tip_amount)

# look at tip percent in df final
df_final %>%
  summarise(
    mean_tip = mean(tip_amount, na.rm = TRUE),
    median_tip = median(tip_amount, na.rm = TRUE),
    mean_tip_pct = mean(tip_pct, na.rm = TRUE),
    median_tip_pct = median(tip_pct, na.rm = TRUE)
  )
```

# Plots
```{r}
theme_taxi <- function() {
  theme_minimal(base_size = 14) +
    theme(
      plot.background = element_rect(fill = "#FFF200", color = NA),  # taxi yellow
      panel.background = element_rect(fill = "white", color = NA),
      panel.grid.major = element_line(color = "grey80", size = 0.3),
      panel.grid.minor = element_blank(),
      
      plot.title = element_text(face = "bold", size = 18, color = "black"),
      axis.title = element_text(face = "bold", color = "black"),
      axis.text = element_text(color = "black"),
      
      axis.line = element_line(color = "black"),
      legend.position = "top"
    )
}

# note: there are several trips where tip is 100 - 700%, but it's uncommon

# Distribution of tip percentage
ggplot(df_final, aes(x = tip_pct)) +
  geom_histogram(
    bins = 100,
    fill = "black",
    color = "#FFF200",
    linewidth = 0.3
  ) +
  labs(
    title = "Distribution of Tip Percentage",
    x = "Tip Percentage",
    y = "Count"
  ) +
  # shrink the x coord because we can't see the outliers anyway
  coord_cartesian(xlim = c(0, 150)) +
  theme_taxi()


# Tip percentage by weekday
# Note: do not filter out outliers on a boxplot - that's the main point
ggplot(df_final, aes(x = pickup_weekday_name, y = tip_pct)) +
  geom_boxplot() +
  labs(
    title = "Tip Percentage by Pickup Weekday",
    x = "Weekday",
    y = "Tip Percentage"
  )+
  theme_taxi()

# Tip percentage vs trip distance
ggplot(df_final, aes(x = trip_distance, y = tip_pct)) +
  geom_point(alpha = 0.1, shape = "o") +
  geom_smooth(method = "lm",
              formula = y ~ splines::bs(x, 3),
              linewidth = 0.9,
              color = "black",
              linetype = "dashed",
              se = FALSE) +
  labs(
    title = "Tip Percentage vs Trip Distance",
    x = "Trip Distance (miles)",
    y = "Tip Percentage"
  )+
  coord_cartesian(xlim = c(0, 10),
                  ylim = c(0, 100)) +
  theme_taxi()

# Tip % vs fare amount
ggplot(df_final, aes(x = fare_amount, y = tip_pct)) +
  geom_point(alpha = 0.1, shape = "o") +
  geom_smooth(
              # formula = y ~ splines::bs(x, 2), 
              linewidth = 0.9,
              color = "black",
              linetype = "dashed",
              se = FALSE) +
  coord_cartesian(xlim = c(0,60),
                  ylim = c(0, 100)) +
  labs(
    title = "Tip Percentage vs Fare Amount",
    x = "Fare Amount",
    y = "Tip Percentage"
  )+
  theme_taxi()
```

# EDA for Tipping Amount
```{r}
# Distribution of tip amount
median_tip <- median(df_final$tip_amount)

ggplot(df_final, aes(x = tip_amount)) +
  geom_histogram(
    bins = 100,
    fill = "black",
    color = "#FFF200",
    alpha = 0.85,
    linewidth = 0.2
  ) +
  geom_vline(
    xintercept = median_tip,
    color = "red",
    linetype = "dashed",
    linewidth = 1
  ) +
  annotate(
    "text",
    x = median_tip,
    y = Inf,
    label = paste0("Median: $", round(median_tip, 2)),
    vjust = 2,
    hjust = -0.1,
    color = "red",
    size = 4,
    fontface = "bold"
  ) +
  coord_cartesian(xlim = c(0, 20)) +
  scale_x_continuous(labels = dollar_format()) +
  labs(
    title = "Distribution of Tip Amount",
    subtitle = "Right-skewed distribution with concentration at low tip values",
    x = "Tip Amount ($)",
    y = "Count",
    caption = "Median tip highlighted with dashed red line"
  ) +
  theme_taxi()

# Tip amount vs fare amount

# These are the outliers in fare amount or tip amount that
# should be highlighted on the plot
df_top <- df_final %>%
  filter(fare_amount > 65 | tip_amount > 20)

ggplot(df_final, aes(x = fare_amount, y = tip_amount,
                     color = tip_amount == 0)) +
  geom_point(alpha = 0.5) +
  geom_smooth(
    method = "lm",
    linewidth = 0.9,
    color = "red",
    linetype = "dashed",
    se = FALSE
  ) +
  geom_text_repel(
    data = df_top,
    aes(label = round(tip_amount, 1)),
    size = 3,
    max.overlaps = 10
  ) +
  coord_cartesian(xlim = c(0, 75), ylim = c(0, 20)) +
  scale_x_continuous(labels = dollar_format()) +
  scale_y_continuous(labels = dollar_format()) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  labs(
    title = "Tip Amount vs Fare Amount",
    subtitle = "Tips increase with fare, but variability remains high",
    x = "Fare Amount ($)",
    y = "Tip Amount ($)",
    caption = "Filtered to typical fare and tip ranges"
  ) +
  theme_taxi() +
  theme(legend.position = "none")

# Tip amount vs trip distance
ggplot(df_final, aes(x = trip_distance, y = tip_amount)) +
  geom_point(alpha = 0.1,
             shape = "o") +
  geom_smooth(method = "lm",
              linewidth = 0.9,
              color = "black",
              linetype = "dashed",
              se = FALSE) +
    coord_cartesian(xlim = c(0,10),
                  ylim = c(0,20)) +
  labs(
    title = "Tip Amount vs Trip Distance",
    x = "Trip Distance (miles)",
    y = "Tip Amount"
  ) +
  theme_taxi()

# Tip amount vs trip duration
ggplot(df_final, aes(x = trip_minutes, y = tip_amount)) +
  geom_point(alpha = 0.1,
             shape = "o") +
  geom_smooth(method = "lm",
              formula = y ~ splines::bs(x, 2),
              linewidth = 0.9,
              color = "black",
              linetype = "dashed",
              se = FALSE) +
  coord_cartesian(xlim = c(0,50),
                  ylim = c(0,20)) +
  labs(
    title = "Tip Amount vs Trip Duration",
    x = "Trip Duration (minutes)",
    y = "Tip Amount"
  ) +
  theme_taxi()
## Comment: Two VERY LONG trips DRASTICALLY changed slope of regression line
```

# See how tip amount varies over time
```{r}
# tip amount over pickup hour (24 hour based)
df_hourly <- df_final %>%
  group_by(pickup_hour) %>%
  summarise(
    median_tip = median(tip_amount, na.rm = TRUE),
    avg_tip = mean(tip_amount, na.rm = TRUE),
    .groups = "drop"
  )

ggplot(df_hourly, aes(x = pickup_hour, y = median_tip)) +
  
  # Line for trend
  geom_line(color = "black", linewidth = 1) +
  # Points for each hour
  geom_point(color = "black", size = 2) +
  geom_smooth(method = "loess", se = FALSE, color = "red", linetype = "dashed") +
  scale_x_continuous(breaks = seq(0, 23, by = 2)) +
  labs(
    title = "Tip Amount by Pickup Hour",
    subtitle = "Median tip peaks around midday",
    x = "Hour of Day (24-hour time)",
    y = "Median Tip Amount ($)",
    caption = "Hourly median tip amounts show minimal variation across the full day"
  ) +
  theme_taxi() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(size = 12),
    plot.caption = element_text(size = 9, color = "black")
  )

# Tip amount by weekday
ggplot(df_final, aes(x = pickup_weekday_name, y = tip_amount)) +
  geom_boxplot() +
  labs(
    title = "Tip Amount by Pickup Weekday",
    x = "Weekday",
    y = "Tip Amount"
  ) +
  theme_taxi()

# Tip amount by weekday -annotated
summary_stats <- df_final %>%
  group_by(pickup_weekday_name) %>%
  summarise(median_tip = median(tip_amount, na.rm = TRUE))

ggplot(df_final, aes(x = fct_relevel(pickup_weekday_name,
                                     "Monday", "Tuesday", "Wednesday",
                                     "Thursday", "Friday", "Saturday", "Sunday"),
                     y = tip_amount)) +
  
  # Boxplot (cleaner look)
  geom_boxplot(fill = "black", color = "#FFF200", outlier.alpha = 0.2, outlier.colour = "black") +
  
  # Add median points for emphasis
  stat_summary(fun = median, geom = "point", color = "#FFF200", size = 2) +
  
  # Optional: jittered points for texture (sample if large dataset)
  # geom_jitter(alpha = 0.05, width = 0.2, color = "#FFF200")
  
  coord_cartesian(ylim = c(0, 20)) +
  
  labs(
    title = "Tip Amount by Day of Week",
    subtitle = "No meaningful variation in tipping behavior across weekdays",
    x = "Day of Week",
    y = "Tip Amount ($)",
    caption = "Median and interquartile ranges are consistent across all days"
  ) +
  
  theme_taxi() +
  
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    plot.caption = element_text(size = 9, color = "black")
  )

# Tip amount by month
df_final %>%
  group_by(month) %>%
  summarise(avg_tip_amt = mean(tip_amount, na.rm = TRUE)) %>%
  ggplot(aes(x = factor(month), y = avg_tip_amt)) +
  geom_col() +
  labs(
    title = "Average Tip Amount by Month",
    x = "Month",
    y = "Average Tip Amount"
  )+
  theme_taxi()

# Tip amount by month - annotated

df_plot <- df_final %>%
  mutate(
    month = factor(month, levels = 1:12, labels = month.abb),
    tourist_season = ifelse(month %in% c("Jul", "Aug", "Oct", "Nov", "Dec"),
                            "Tourist Season", "Non-Tourist Season")
  ) %>%
  group_by(month, tourist_season) %>%
  summarise(avg_tip_amt = mean(tip_amount, na.rm = TRUE), .groups = "drop")

ggplot(df_plot, aes(x = month, y = avg_tip_amt, fill = tourist_season)) +
  
  geom_col(color = "black", width = 0.7) +
  
  scale_fill_manual(
    values = c(
      "Tourist Season" = "gray",
      "Non-Tourist Season" = "gray30"
    )
  ) +
  
  labs(
    title = "Average Tip Amount by Month",
    subtitle = "Tourist seasons (Jul–Aug, Oct–Dec) show no substantial increase in tipping",
    x = "Month",
    y = "Average Tip Amount ($)",
    fill = "",
    caption = "Differences across months are minimal despite seasonal travel patterns"
  ) +
  
  theme_taxi() +
  
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(size = 12),
    axis.text.x = element_text(angle = 30, hjust = 1),
    legend.position = "top",
    plot.caption = element_text(size = 9, color = "black")
  )
```

# Look at Tourist Season: July, Oct-Dec
```{r}
# Tip amount vs tourist season
df_final %>%
  group_by(tourist_season) %>%
  summarise(avg_tip_amt = mean(tip_amount, na.rm = TRUE)) %>%
  ggplot(aes(x = factor(tourist_season), y = avg_tip_amt)) +
  geom_col() +
  labs(
    title = "Average Tip Amount by Tourist Season",
    x = "Tourist Season",
    y = "Average Tip Amount"
  )+
  theme_taxi()

# Tip amount vs tourist season - higher amounts are more common in tourist season
df_final %>%
  ggplot(aes(x = tip_amount, color = factor(tourist_season))) +
  geom_density(linewidth = 0.75) +
  labs(
    title = "Tip Amount Dist in Tourist Season vs Off-Season",
    x = "Tip Amount",
    color = "Tourist Season"
  ) +
  theme_taxi()

# Tip percent vs tourist season - does not seem to vary by tourist season
df_final %>%
  ggplot(aes(x = tip_pct, color = factor(tourist_season))) +
  geom_density(linewidth = 0.75) +
  ggtitle("Tip Percent Dist in Tourist Season vs Off-Season") +
  xlab("Tip Percent") +
  theme_taxi()
```


# Looking at Correlation Among Numerical Predictors
```{r}
numeric_vars <- df_final %>%
  select(
    fare_amount,
    trip_distance,
    extra,
    pickup_hour,
    dropoff_hour,
    trip_minutes,
    trip_speed_mph,
    tip_amount,
    pickup_weekday_num,
    total_amount
    # tourist_season
  )

cor_matrix <- cor(numeric_vars, use = "pairwise.complete.obs")
cor_matrix

# Heatmap Version
corrplot::corrplot(cor_matrix, method = "color", type = "upper")

plot_correlation(numeric_vars)
```


# MODELING

### Cleaning
```{r}
# Listing Columns
names(df_final)

# Clean obvious bad records before modelingd 
df_clean <- df_final %>%
  filter(
    tip_amount > 0, 
    tip_amount < quantile(tip_amount, 0.99),
    # fare_amount > 0, # already filtered in original data clenaing
    # total_amount > 0, # already filtered in original data clenaing
    trip_distance > 0,
    trip_minutes > 0
  )

 df_clean = df_clean %>% mutate(
    month = factor(month),
    pickup_hour = factor(pickup_hour),
    pickup_weekday_name = factor(pickup_weekday_name, ordered = FALSE))

# Creating DF subset
df_model1 = df_clean %>% 
  select(tip_amount,
         fare_amount,
         total_amount,
         trip_distance,
         extra,
         trip_minutes
         # month,
         # tourist_season
         )

```

### MODEL 1
```{r}
set.seed(123)

fit1 <- lm(log(tip_amount)~fare_amount +
                          I(fare_amount^2) +
                          trip_distance +
                          extra +
                          trip_minutes,
                          data = df_model1)
summary(fit1)

# trip_distance & trip_minutes are not seen as significant predictors so we will remove
```

### MODEL 2
```{r}
fit2 <- lm(log(tip_amount)~fare_amount + 
                          I(fare_amount^2)  + 
                          extra,
                          data = df_model1)
summary(fit2)

# Assumptions
par(mfrow = c(2, 2))
plot(fit2)
par(mfrow = c(1, 1))


# Interaction Needed?

# model without interaction
fit2 <- lm(log(tip_amount)~fare_amount + 
                          I(fare_amount^2)  + 
                          extra,
                          data = df_model1)

# model with interaction
fit_int <- lm(log(tip_amount)~fare_amount + 
                          I(fare_amount^2)  + 
                          extra + fare_amount*extra,
                          data = df_model1)
# is interaction neccesary?
anova(fit2, fit_int)
# yes significant p-value when added however RSS drop does not seem significant enough to hurt parsimony of model so we will proceed without
```

# Comparing Metrics With Interaction vs Without
```{r}
# predicted values on log scale
pred_log_2 <- predict(fit2)
pred_log_i <- predict(fit_int)

# back-transform to original dollar scale
pred_tip_2 <- exp(pred_log_2)
pred_tip_i <- exp(pred_log_i)

# RMSE on original scale
rmse_2 <- sqrt(mean((df_model1$tip_amount - pred_tip_2)^2))
rmse_2

rmse_i <- sqrt(mean((df_model1$tip_amount - pred_tip_i)^2))
rmse_i

# MAE on original scale
mae_2 <- mean(abs(df_model1$tip_amount - pred_tip_2))
mae_2

mae_i <- mean(abs(df_model1$tip_amount - pred_tip_i))
mae_i
```

# Seeing if there any signficant outliers
```{r}
# studentized residuals, leverage, Cook's distance
rstud <- rstudent(fit1)
lev   <- hatvalues(fit1)
cd    <- cooks.distance(fit1)

n <- nrow(model.frame(fit1))
p <- length(coef(fit1))

# stricter flags
which(abs(rstud) > 3)       # strong residual outliers
which(lev > 3 * p / n)      # higher leverage cutoff
which(cd > 1)               # very influential points

# top 10 by Cook's distance
head(order(cd, decreasing = TRUE), 10)

# top 10 by absolute studentized residual
head(order(abs(rstud), decreasing = TRUE), 10)

# top 10 by leverage
head(order(lev, decreasing = TRUE), 10)


idx <- unique(c(
  head(order(cd, decreasing = TRUE), 10),
  head(order(abs(rstud), decreasing = TRUE), 10),
  head(order(lev, decreasing = TRUE), 10)
))

df_o = df_clean[idx, ] # other outliers due to tip pct% being SO small even with larger fare amounts. We will keep in model
df_o1 = df_clean[c(1902, 4805,2217),]
# Nothing out of the ordinary is being displayed outliers so we will keep them in the model
```


### MODEL 3 - Cleaning for Typical Cases (Did not end up using cuz of overfitting concerns)
```{r}
# df_typical <- df_final %>%
#   mutate(tip_pct = tip_amount / fare_amount) %>%
#   filter(
#     tip_amount > 0,
#     # fare_amount > 0, # already filtered in original data cleaning
#     # total_amount > 0, # already filtered in original data cleaning
#     # trip_distance > 0, # already filtered in modeling data cleaning
#     # trip_minutes > 0, # already filtered in modeling data cleaning
#     between(fare_amount, quantile(fare_amount, 0.01), quantile(fare_amount, 0.99)),
#     between(total_amount, quantile(total_amount, 0.01), quantile(total_amount, 0.99)),
#     between(trip_distance, quantile(trip_distance, 0.01), quantile(trip_distance, 0.99)),
#     between(trip_minutes, quantile(trip_minutes, 0.01), quantile(trip_minutes, 0.99)),
#     between(tip_pct, quantile(tip_pct, 0.01), quantile(tip_pct, 0.99))
#   )
# 
# fit2 <- lm(
#   log(tip_amount) ~ total_amount +
#     I(total_amount^2) +
#     extra,
#   data = df_typical
# )
# summary(fit2)
# 
# # Assumptions
# par(mfrow = c(2, 2))
# plot(fit2)
# par(mfrow = c(1, 1))
# 
# 
# # predicted values on log scale
# pred_log <- predict(fit2)
# 
# # back-transform to original dollar scale
# pred_tip <- exp(pred_log)
# 
# # RMSE on original scale
# rmse <- sqrt(mean((df_typical$tip_amount - pred_tip)^2))
# rmse
# 
# # MAE on original scale
# mae <- mean(abs(df_typical$tip_amount - pred_tip))
# mae
```